Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2014-10-24 Report/decomposition_solutions.tex
Submitted version

This section addresses the distributed precoder designs for the proposed \ac{JSFRA} scheme. The formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}. In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are considered. In particular, the \acl{PD} and the \ac{ADMM} based \acl{DD} approaches are addressed.

To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}. In order to study the decomposition based solutions, we consider the solution proposed in \eqref{eqn-9}, which is based on the Taylor series approximation for the nonconvex constraint. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
{\allowdisplaybreaks
\begin{IEEEeqnarray}{CCl} \label{eqn-decent-1}
\underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e}, \IEEEyessubnumber
\end{IEEEeqnarray}}
where \me{\tilde{\mbf{v}}_b} denotes the vector of of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.

>>>>

This section addresses the distributed precoder designs for the proposed \ac{JSFRA} scheme. The formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the \acp{BS} in \me{\mc{B}}. In order to design the precoders independently at each \ac{BS} with the minimal information exchange via back-haul, iterative decentralization methods are considered. In particular, the \acl{PD} and the \ac{ADMM} which is basically based on \acl{DD} approaches are followed in this paper.

To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}. To facilitate decomposition based solutions, we consider the solution proposed in \eqref{eqn-9}, which is based on the Taylor series approximation for the nonconvex constraint. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
{\allowdisplaybreaks
\begin{IEEEeqnarray}{CCl} \label{eqn-decent-1}
\underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e}, \IEEEyessubnumber
\end{IEEEeqnarray}}
where \me{\tilde{\mbf{v}}_b} denotes the vector of of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.

### 2014-10-24 Report/ieee_journal.tex
final_submission_text
final version
Submitted version

\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}

@@

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland. Part of this work has been published in ICASSP 2014 conference.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}

@@

\begin{IEEEkeywords}
\ac{MIMO}-\ac{OFDM}, Queue minimizing precoder design, \acs{SCA}, Convex approximation.
\end{IEEEkeywords}

@@

\acresetall
\section{Conclusions} \label{sec-6}
\input{conclusions}

>>>>

\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}

@@

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman\IEEEauthorrefmark{1} \thanks{This work is supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland. Part of this work has been published in ICASSP 2014 conference.} \IEEEmembership{Student Member,~IEEE}, Antti T\"{o}lli\IEEEauthorrefmark{1} \IEEEmembership{Member,~IEEE}, Le-Nam Tran\IEEEauthorrefmark{2} \thanks{\IEEEauthorrefmark{2}Dr. L.-N. Tran is associated with the Department of Electronic Engineering, Maynooth University, Co. Kildare, Irealand, e-mail:ltran@eeng.nuim.ie} \IEEEmembership{Member,~IEEE}, and Markku Juntti\IEEEauthorrefmark{1} \IEEEmembership{Senior Member,~IEEE}}\thanks{\IEEEauthorrefmark{1}The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi).}}

@@

\begin{IEEEkeywords}
convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \ac{WSRM}.
\end{IEEEkeywords}

@@

%acresetall
\section{Conclusions} \label{sec-6}
\input{conclusions}

### 2014-10-24 Report/introduction.tex
Submitted version

In a network with multiple \acp{BS} serving \acp{MU}, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network. These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints. We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets. Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.

In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence in a particular resource \cite{admission_control}. In contrast to that, we use linear transmit precoders, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource. The purpose is two-fold. Firstly, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.

@@

The connection between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} can also be used to solve the \ac{WSRM} problem. In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders. Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the remaining others are fixed. The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner. Additional rate constraints based on the \ac{QoS} requirements were included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.

The problem of precoder design for the \ac{MIMO} \ac{IBC} system are solved either by using a centralized controller or by using decentralized algorithms where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with the other \acp{BS} via back-haul. The distributed approaches are based on primal, dual or \ac{ADMM} decomposition, which has been discussed in \cite{palomar2006tutorial,boyd2011distributed}. In the  primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders. The fixed interference are then updated by using the subgradient method as discussed in \cite{pennanen2011decentralized}. The dual and \ac{ADMM} approaches control the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.

By adjusting the weights in the \ac{WSRM} objective properly, we can find an arbitrary rate-tuple in the rate region that maximizes the suitable objective measures. For example, if the weight of each user is set to be inversely proportional to its average data rate, the corresponding problem guarantees fairness on an average among the users. As an approximation, we may assign weights based on the current queue size of the users. More specifically, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}. In backpressure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.

@@

\subsubsection*{Main Contributions}
In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}. Since the problem is nonconvex, we adopt the \ac{SCA} technique to solve by a sequence of convex subproblems using first order approximations. Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} technique for the nonconvex constraints. First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders. Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods. Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.

>>>>

In a network with multiple \acp{BS} serving \acp{MU}, the main driving factor for downlink transmission is the number of  packets waiting at each \ac{BS} corresponding to the different users present in the network. These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints. We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets. Since the space-frequency resources are shared by multiple users in different \acp{BS}, it can be viewed as a resource allocation problem.

In general, the resource allocation problems are formulated by assigning a binary variable for each user to indicate whether the user is allocated to a particular resource \cite{admission_control}. In this paper, we follow a different approach in which linear transmit precoders are used as decision variables. The purpose is two-fold. Firstly, it determines the transmission rate on a particular resource. Secondly, in certain resource, if the transmit precoder of a user turns out to be a zero vector after solving the design problem, the corresponding user will not be scheduled.

@@

The connection between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} can also be used to solve the \ac{WSRM} problem. In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients. In this way, the original problem is expressed in terms of the \ac{MSE} weights, precoders, and decoders. Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the remaining others are fixed. The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner. Additional rate constraints based on the \ac{QoS} requirements were included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.

The problem of precoder design for the \ac{MIMO} \ac{IBC} system is solved either by using a centralized controller or by using decentralized algorithms where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with the other \acp{BS} via back-haul. The distributed approaches are based on primal, dual or \ac{ADMM} decomposition, which has been discussed in \cite{palomar2006tutorial,boyd2011distributed}. In the  primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders. The fixed interference are then updated by using the subgradient method as discussed in \cite{pennanen2011decentralized}. The dual and \ac{ADMM} approaches control the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.

By adjusting the weights in the \ac{WSRM} problem properly, we can find a rate-tuple in the rate region that maximizes a performance measure of interest. For example, if the weights of each user is set to be inversely proportional to user's average data rate, the problem guarantees fairness on average achieved rate among the users. As an approximation to our considered problem, we may assign weights based on the current queue size of the users. More specifically, the queue states can be incorporated to the traditional \ac{WSRM} objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a related function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}. In backpressure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.

@@

\subsubsection*{Main Contributions}
In this paper, we design the precoders jointly across space-frequency resources to minimize the total number of backlogged packets waiting at the \acp{BS}. Since the problem is nonconvex, we adopt the \ac{SCA} technique to solve by a sequence of convex subproblems using first order approximations. First, we propose two centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} technique for the nonconvex constraints. The first method is based on applying the \ac{SCA} technique to the nonconvex constraints of the problem formulation directly, while the second one applies \ac{SCA} technique to the equivalent formulation obtained by the \ac{MSE} equivalence. In the second part, we propose a distributed precoder designs based on the primal and the \ac{ADMM}. Finally, we propose an iterative algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.

### 2014-10-24 Report/joint_wsrm_formulation.tex
Submitted version

The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network. One such algorithm  is the \emph{backpressure algorithm} \cite{tassiulas,georgiadis2006resource,neely2010stochastic}. It determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes. Even though the algorithm is primarily designed for the wired infrastructure, it can be extended to the wireless networks by designing the user rate variable \me{t_k} in accordance to the wireless network.

@@

The expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the number of backlogged packets corresponding to the users. The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders. Since the expectation can be minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by 
\begin{IEEEeqnarray}{LCl} \label{q_gen_sum}
	\underset{\substack{\mvec{M}{k,n}, \mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
	\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-3.1.3}
\end{IEEEeqnarray}

In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}. The rate constrained version of the \ac{Q-WSRM}, denoted by \ac{Q-WSRME} problem for a cellular system, is given by \label{q_gen_sum-1} with the additional constraint
\begin{IEEEeqnarray}{rCl} \label{eqn-3.1.4}
\sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U},
\end{IEEEeqnarray}
where the precoders are associated with \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}. By using the number of queued packets as the weights, the resources can be allocated to the user with the more backlogged packets, which essentially does the allocation in a greedy manner.

As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}. This approach provides a greedy queue minimizing allocation as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison to the number of queued packets as in \ac{Q-WSRME}. Note that in both formulations, the resources allocated to the users are limited by the number of backlogged packets with an explicit maximum rate constraint defined by \eqref{eqn-3.1.4}.

>>>>

The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network. One such algorithm  is the \emph{backpressure algorithm} \cite{tassiulas,georgiadis2006resource,neely2010stochastic}. It determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes. Even though the algorithm is primarily designed for wired infrastructures, it can be extended to wireless networks by designing the user rate variable \me{t_k} in accordance to wireless networks.

@@

The expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the number of backlogged packets corresponding to the users. The above discussed approach was extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders. Since the expectation can be minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by 
\begin{IEEEeqnarray}{LCl} \label{q_gen_sum}
	\underset{\substack{\mvec{M}{k,n}, \mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
	\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-3.1.3}
\end{IEEEeqnarray}

In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}. The rate constrained version of the \ac{Q-WSRM}, denoted by \ac{Q-WSRME} problem for a cellular system, is given by \label{q_gen_sum-1} with the additional constraint
\begin{IEEEeqnarray}{rCl} \label{eqn-3.1.4}
\sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U},
\end{IEEEeqnarray}
where the precoders are associated with \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}. By using the number of queued packets as the weights, the resources can be allocated to users with more backlogged packets, which essentially a greedy resource allocation scheme.

As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} to be unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}. This approach provides a greedy queue minimizing allocation as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison to the number of queued packets as in \ac{Q-WSRME}. Note that in both formulations, the resources allocated to the users are limited by the number of backlogged packets with an explicit maximum rate constraint given in \eqref{eqn-3.1.4}.

### 2014-10-24 Report/kkt_mse_approach.tex
Submitted version

The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which are obtained by the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}. Upon solving, we obtain the iterative solution as

@@

To devise an algorithm for a practical implementation, we extend the decentralization methods discussed in \cite{komulainen2013effective}, for our problem of minimizing the total number of backlogged packets as follows. After receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user evaluates the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify them to the \acp{BS} via uplink precoded pilots. On receiving pilot signals, \acp{BS} update the \ac{MSE} in \eqref{mse-error} as 
\begin{equation}
\epsilon_{l,k,n}^{(i)} = 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)}.
\end{equation}
Using the current \ac{MSE} value, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}, and the updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration. The \ac{SCA} operating point is also updated with the current \ac{MSE} value.

>>>>

The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which are obtained by the derivative of the Lagrangian function w.r.t the primal variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}. Upon solving, we obtain the iterative solution as

@@

To devise an algorithm for a more practical implementation, we extend the decentralization methods discussed in \cite{komulainen2013effective}, for our problem of minimizing the total number of backlogged packets as follows. After receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user evaluates the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify them to the \acp{BS} via uplink precoded pilots. On receiving pilot signals, \acp{BS} update the \ac{MSE} in \eqref{mse-error} as 
\begin{equation}
\epsilon_{l,k,n}^{(i)} = 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)}.
\end{equation}
Using the current \ac{MSE} value, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}, and the updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration. The \ac{SCA} operating point is also updated with the current \ac{MSE} value.

### 2014-10-24 Report/mse_formulation.tex
Submitted version

In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
\iftoggle{single_column}{
\begin{multline} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
	+ \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
\end{multline}
}{
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
\end{multline}
}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}},
\end{equation}
where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.

>>>>

In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for \ac{MMSE} receivers \cite{viswanath1999optimal,mse_duality}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
\iftoggle{single_column}{
\begin{multline} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
	+ \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
\end{multline}
}{
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
\end{multline}
}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}},
\end{equation}
where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.
